Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-19 paper/icml_drau/advup.tex
relecture experiments

In what follows, a discrete algorithm with a well defined time continuous
limit is defined. The algorithm relies on three elements, namely, defining and
learning a quantity that contains some information on the ranking of actions
while admitting a time continuous limit, defining exploration methods that
admit a continuous time limit and defining learning rates that induce well
behaved parameter trajectories when $\deltat$ goes to $0$.

As seen in Sec.~\ref{sec:framework}, there is no continuous time limit to
Q-learning. In continuous time, $Q^\pi$ is independent of actions and can thus
not be used to select promising actions.  In near continuous time, $Q^\pi_\deltat$
still depends on actions, and can still be used to choose promising actions
under the current policy. However, when approximating $Q^\pi_\deltat$, if the
approximation error is much bigger than $\bigO(\deltat)$, approximation errors
dominates, and the ranking of actions given by the approximation is likely to
be erroneous.
% When the approximate Q-function is initialized, if the effect of
% actions on the Q-function is order of magnitudes higher than what it should be,
% approximating $Q^\pi_\deltat$ is likely to be difficult.
%Besides, the error is likely
%to be further propagated when the equation used to update our approximate $Q$
%function relies on bootstraping, as is the case for usual temporal difference
%derived methods.

@@

% With this choice of learning rates, the limit SDEs are
% \begin{align}
% 	F &= A(s_t, a_t) - r_t - \log(\gamma) V(s_t) - \partial_s V(s_t) f(s_t, a_t)\nonumber\\
% 	G &= - \partial_s V(s_t, a_t) \Sigma(s_t, a_t)\nonumber\\
% 	d\theta_t &= (\alpha^V Fdt  + D \dbt)\partial_{\theta} V(s_t)\nonumber\\
% 	d\psi_t &= (\alpha^A Fdt  + D \dbt)\partial_{\psi} A(s_t, a_t)\nonumber.
% \end{align}
The full algorithm can now be derived.
Pseudocode for the discrete actions algorithm is given in Alg.~\ref{alg:dau}.
Pseudocode for the continuous actions algorithm is given in the supplementary
material.

>>>>

We now define a discrete algorithm with a well-defined continuous-time
limit.  It relies on three elements: defining and learning a quantity
that still contains information on action rankings in the limit, using
exploration methods with a meaningful limit, and scaling learning rates
to induce well-behaved parameter trajectories when $\deltat$ goes to $0$.

As seen above, there is no continuous time limit to Q-learning. In
continuous time, $Q^\pi$ is independent of actions and can thus not be
used to select promising actions.  In near-continuous time,
$Q^\pi_\deltat$ still depends on actions, and could still be used to
choose promising actions under the current policy. However, when
approximating $Q^\pi_\deltat$, if the approximation error is much bigger
than $\bigO(\deltat)$, approximation errors dominates, and the ranking of
actions given by the approximation is likely to be erroneous.

% When the approximate Q-function is initialized, if the effect of
% actions on the Q-function is order of magnitudes higher than what it should be,
% approximating $Q^\pi_\deltat$ is likely to be difficult.
%Besides, the error is likely
%to be further propagated when the equation used to update our approximate $Q$
%function relies on bootstraping, as is the case for usual temporal difference
%derived methods.

@@

% With this choice of learning rates, the limit SDEs are
% \begin{align}
% 	F &= A(s_t, a_t) - r_t - \log(\gamma) V(s_t) - \partial_s V(s_t) f(s_t, a_t)\nonumber\\
% 	G &= - \partial_s V(s_t, a_t) \Sigma(s_t, a_t)\nonumber\\
% 	d\theta_t &= (\alpha^V Fdt  + D \dbt)\partial_{\theta} V(s_t)\nonumber\\
% 	d\psi_t &= (\alpha^A Fdt  + D \dbt)\partial_{\psi} A(s_t, a_t)\nonumber.
% \end{align}
The full algorithm, that is referred to as \emph{Deep Advantage Updating} (DAU), can now be derived.
Pseudocode for the discrete actions algorithm is given in Alg.~\ref{alg:dau}.
Pseudocode for the continuous actions algorithm is given in the supplementary
material.
